### 2019-03-17 papers/journal/encoding.tex
minor update
added the combi. problem subsection
update in BMC section

The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding slightly in the way variables are represented and how we encode reachability.  
%
In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
%
Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%
The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
%

The molecule set is divided into Q and R-SNAREs. 
%
For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
%
Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
%
Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
%
For example, the variable \texttt{bvEdge}[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present.

Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
%
We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%
Here, we will only present the stability encoding.  
%
Rest of the encoding are similar to the one presented in the Section~\ref{enc:smt}.

@@

\subsection{Universal condition}
\label{enc:univ-cond}
%
Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%

\input{satqbf-table}
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.

\textbf{$\fqbf$ encoding of the universal condition:}
We will describe several constraints that encode VTSs in this section.
%
To avoid cumbersome notation, we will not explicitly write the ranges
of the indexing in the constraints.
%
$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
%
$m$ will range over molecules, i.e., from $1$ to $\mu$.
%
$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
%

>>>>

The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding slightly in the way variables are represented and how we encode reachability.  
%
Here, we will only present the stability encoding.  
%
Rest of the encoding are similar to the one presented in the previous section, Section~\ref{enc:smt}.

In the $\fbmc$ encoding, variables are represented as an array of bit vectors of size $M$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
For example, every edge is represented as a bit vector of size $M$ with each bit corresponding to the presence or absence of the molecule. 
%
Bit vector \texttt{bvEdge}$[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%
The index of the bit vector implicitly determines the corresponding molecule we are referring to in the edge.
%

The molecule set is divided into Q and R-SNAREs. 
%
For clarity, we consider the first part of the bit vector as Q-SNAREs and rest as R-SNAREs.
%
An edge in the system with $M$ = 4 molecules is interpreted as a label [$M_{1}, M_{2}, M_{3}, M_{4}$]. 
%
Where $M_{1}, M_{2}, M_{3}$ are Q-SNAREs while $M_{4}$ is a R-SNARE.
%
Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the $i^{th}$ molecule.
%
For example, the variable \texttt{bvEdge}[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule $M_{1}$ (Q-SNARE) and $M_{4}$ (R-SNARE) present. 
%
Similarly, a node in the graph is also labelled as a bit vector of length $M$.   
%
We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%

@@

\subsection{Universal condition}
\label{enc:univ-cond}
%
Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version of the universal problem extending the current $\fsmt$ search encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%
%
\input{satqbf-table}
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
%

\textbf{$\fqbf$ search encoding of the universal condition:}
We will describe several constraints that encode VTSs in this section.
%
To avoid cumbersome notation, we will not explicitly write the ranges
of the indexing in the constraints.
%
$i$ and $j$ will range over nodes, i.e., from $1$ to $\nu$.
%
$m$ will range over molecules, i.e., from $1$ to $\mu$.
%
$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
%
